Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

K-S statistic are obtained by finding the furthest vertical distance between the two CDFs as indicated by the arrows. The greater the distance, the more likely it is that two CDFs are from two different distributions so that it can be an indication that there has been a change on performance.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.4\textwidth]{resources/ch2/ks.png}
	\caption{CDF of two samples, arrows indicate the Kolmogorov-Smirnov statistical value \cite{wiki:ks-test}}
	\label{ks-example}
\end{figure}

@@

Fig. \ref{flow-pra} illustrates the phases to be carried out by the PRA system. In general, there will be two phases to be carried out, namely the baseline loading phase
and the periodic analysis phase. The first phase, namely the loading phase, will look for stable application activity data that can be used as a baseline or a reference for the analysis to be carried out in the next stages. This phase
will produce two artifacts, the latency data of all recorded traces by the tracing system, and operating data that occurs on the critical path of all traces along with its latency value which will be stored as a key-value pair as well.

@@

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth,scale=5]{resources/ch3/alur_v2.png}
	\caption{PRA system flow}
	\label{flow-pra}
\end{figure}

\subsection{Architecture}
Fig. \ref{arch-pra} shows the architecture of the PRA system. There will be only two components that will be implemented from scratch, which are the PRA Engine and the PRA UI. The rest of the components are already present and ready to use from Zipkin. The PRA Engine will implement the logic from Fig \ref{flow-pra} and will be exposed as an Application Programming Interface (API). The PRA UI will fetch data from the PRA Engine API and will present the state of regression in the application, and the critical path analysis result.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.4\textwidth]{resources/ch3/arch.png}
	\caption{PRA system architecture}
	\label{arch-pra}
\end{figure}

>>>>

K-S statistic are obtained by finding the furthest vertical distance between the two CDFs as indicated by the arrows. The greater the distance, the more likely it is that two CDFs are from two different distributions so that it can be an indication that there has been a change on performance.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.35\textwidth]{resources/ch2/ks.png}
	\caption{CDF of two samples, arrows indicate the Kolmogorov-Smirnov statistical value \cite{wiki:ks-test}}
	\label{ks-example}
\end{figure}

@@

Fig. \ref{flow-pra} illustrates the phases to be carried out by the PRA system. In general, there will be two phases to be carried out, namely the baseline loading phase
and the periodic analysis phase. The first phase, namely the loading phase, will look for stable application activity data that can be used as a baseline or a reference for the analysis to be carried out in the next stages. This phase
will produce two artifacts, the latency data of all recorded traces by the tracing system, and operating data that occurs on the critical path of all traces along with its latency value which will be stored as a key-value pair as well.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth,scale=5]{resources/ch3/alur_v2.png}
	\caption{PRA system flow}
	\label{flow-pra}
\end{figure}

@@

\subsection{Architecture}
Fig. \ref{arch-pra} shows the architecture of the PRA system. There will be only two components that will be implemented from scratch, which are the PRA Engine and the PRA UI. The rest of the components are already present and ready to use from Zipkin. The PRA Engine will fetch data from Zipkin API to retrieve the traces generated and will implement the logic from Fig \ref{flow-pra}. The PRA Engine will be exposed as an Application Programming Interface (API). The PRA UI will fetch data from the PRA Engine API and will present the state of regression in the application, and the critical path analysis result.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.4\textwidth]{resources/ch3/arch.png}
	\caption{PRA system architecture}
	\label{arch-pra}
\end{figure}
